quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-13 paper-quollr.Rmd
Added low-density removal to front

@@

ggplot() + 
  geom_hexgrid(
    data = df_bin_centroids, 
    aes(x = c_x, y = c_y)
    ) 
```

@@

@@

```{r, echo=TRUE, eval=knitr::is_html_output()}
trimesh <- trimesh |>
  dplyr::filter(from_count > 10,
                to_count > 10)

show_langevitour(
  point_data = df_exe, 
  edge_data = trimesh
  )
```

>>>>

For simplicity, we remove low-density hexagons using a threshold of $10$.

trimesh <- trimesh |>
  dplyr::filter(from_count > 10,
                to_count > 10)

@@

```{r, echo=TRUE}
ggplot() + 
  geom_hexgrid(
    data = df_bin_centroids, 
    aes(x = c_x, y = c_y)
    ) 
```

@@

```{r, echo=TRUE}

@@

```{r, echo=TRUE, eval=knitr::is_html_output()}
show_langevitour(
  point_data = df_exe, 
  edge_data = trimesh
  )
```

### 2025-05-13 paper-quollr.tex
Added low-density removal to front

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-21-1}

@@

ggplot() + 
  geom_hexgrid(
    data = df_bin_centroids, 
    aes(x = c_x, y = c_y)
    ) 
\end{verbatim}

@@

@@

df_exe <- comb_data_model(
  highd_data = scurve, 
  model_highd = df_bin, 
  model_2d = df_bin_centroids
  )

@@

\begin{verbatim}
trimesh <- trimesh |>
  dplyr::filter(from_count > 10,
                to_count > 10)

trimesh <- update_trimesh_index(trimesh)

show_langevitour(
  point_data = df_exe, 
  edge_data = trimesh
  )
\end{verbatim}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-32-1}

>>>>

For simplicity, we remove low-density hexagons using a threshold of \(10\).

trimesh <- trimesh |>
  dplyr::filter(from_count > 10,
                to_count > 10)

trimesh <- update_trimesh_index(trimesh)
\end{verbatim}

@@

@@

\begin{verbatim}
ggplot() + 
  geom_hexgrid(
    data = df_bin_centroids, 
    aes(x = c_x, y = c_y)
    ) 
\end{verbatim}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-25-1}

@@

\begin{verbatim}
df_exe <- comb_data_model(
  highd_data = scurve, 
  model_highd = df_bin, 
  model_2d = df_bin_centroids
  )

@@

\begin{verbatim}
show_langevitour(
  point_data = df_exe, 
  edge_data = trimesh
  )
\end{verbatim}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-33-1}
